% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title
\title{CPD Report}

% Please do not change the subtitle
\subtitle{COMP160 - CPD Report}

% Please put your student number in the author field
\author{1605240}

\begin{document}

\maketitle

\section*{Introduction}
The end of our second semester and first year of university has come by quicker than I could have imagined, therefore I am having to write about my personal development over this term. I have written a brief description of what I did every week and the problems I have faced. I have identified the five main problems I was having throughout the term and will write about them in this report. I think doing this can have a huge benefit if you actually follow through with what you say you'll do as when comparing them back to my last CPD report I believe I have had a good improvement on four out of the five skills I identified last term.

\section{Communication}
The biggest problem in my opinion for me this term was communication between team members for the group game we had to make. I feel as if the majority of the team communications skills lacked including my own. We had team members consistently not replying when we messaged them which in turn led to us falling behind as all team members are vital in a group project. To improve on this for next term I plan to make sure my new team actually feel like a team by socializing with them out with of university as I feel it'll help bring us closer together and help us get along better. I want everyone to know they play a huge role in the team and if we all help each other we can successfully make a good game if we all just try our best.


\section{C++}
Although C++ plays a large part in game development I feel as if I don't know my fair share of it, that is why I have chosen this as my second skill I plan to improve on. This term we got introduced to a new programming language which was C++, I followed some basic Plural Sight tutorials and read up on information I needed in order to do the worksheets but apart from that I didn't do much else with it. I am disappointed in myself for this as I really want to learn more of it and expand my knowledge of coding and different languages too in general. However the university computers didn't work too well when using C++ in Unreal as it crashed most of the time or took too long to compile. I plan to work on this over summer and try to teach myself how to make some basic programs and learn the benefits of using it in Unreal Engine, I will also throughly read through the C++ text book we had to buy.


\section{Problem Solving}
Problem solving skills play a large part in programming especially when it comes to small things like fixing bugs. My problem solving skills have never been as strong as I'd like them to be. This term I struggled quite a lot with a few aspects of work involving problem solving. I always search the web for help and try my best at attempting to do whatever it is I'm doing and if I can't find the answer I usually get stressed. Instead of doing this I should ask my fellow peers or lecturers for help more often as sometimes it's the smallest of mistakes which can cause the biggest problems. To improve this I am going to ask for help more often as it'll save me time searching for so long and will help me know for next time if I face the same issue.

\section{Balancing My Workload}
During this term I struggle with balancing my workload. By this I mean I would just do the same task even if I couldn't get it working and I would work on the same task until it was finished even if it took several days, this isn't good as I feel as if I should limit myself to one task for a certain time before asking for help and I need to know when to move onto the next task. I feel this has potentially limited my grades in certain modules as I spent too much time on other modules in comparison, to help my with this problem for next term I plan to buy myself a wall calendar and schedule my days around university and plan what I'm doing every day. I think this will help as I do better with visual aids instead of telling myself to do something.


\section{Game Engines}
This term introduced us to Unreal Engine for the first time at university, I was amazed with how easy the interface was to follow. Although is has a nice interface the amount of features it offer is very vast and would take thousands of hours to master them all. This is an industry standard tool which means it is used in actual game development which is good as we are getting lots of experience using it. I have only been using the blueprints it offers to program with but I wish to expand to using C++ as well as well as learning the basics of most of the other features to have a simple understanding of what everything does. This will help me improve my knowledge of Unreal greatly while forcing me to learn small areas of other game design paths which will look good on my CV. To do this I plan to make my own game where I create most if not everything myself while following tutorials to learn from.


\section*{Conclusion}
Through this report I identified five key skills that will help me progress as a better university student as well as helping me become a better game developer in the future I just have to make sure I stick to them and progress as that's what the point of this report is to do. I am hoping that when I come back to university after Summer I have already started improving on these skills especially my knowledge of C++ and the Unreal Engine and I plan to be working on the others as well as making sure I am still following my skills from my last CPD report as it would be like going one step forward and two steps backwards.


\bibliographystyle{ieeetran}
\bibliography{references}

\end{document}